The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes

### 2023-04-05 hw1/paper/main.tex
, add space

  \bf{neural network}:

  \bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most likely outcome according to the conditional probability it just recorded.

@@

\section{neural network}

\section{Naive Bayes classifier}

>>>>

  \bf{neural network}: \rm{Neural} network have been used in many fields to deal with intricate datas.With input layer, hidden layer and output layer constructed by neurons, each data in dataset is processed while passing through neurons, layer by layer.After the processing, the outcome can be used to predict.Using back propogation, the accuracy of predictions increase in each training.In order to construct the hidden layer more efficient, NAS(Neural Arcitecture Searching) is used to search suitable structure for hidden layer, increasing the accuracy.According to \cite{Gadekallu2020}\cite{Beghriche2021}, many neural network have been constructed and trained already, with high efficiency and accuracy in prediction of diabetes.

  \bf{naive Bayes classifier}:

@@

\section{neural network}
Given a dataset $D$ containing $N$ data points and a label with $0$ or $1$ representing the patient is diagnosed with diabetes or not, we need to construct a model with $N$-neurons input layer and 2-neurons output layer.Before we construct the model, we have to find the structure of the hidden layer with NAS.
We set the number of the layer to 10, with each layer has more than 16 and less than 256 neurons.Define the search space $\mathcal{F}$, which including all the arrays including 10 numbers and each of the number in the array represents the number of neurons in each layers, which is more then 16 and less than 256, like above.We are aiming to find the approximate solution $f= \{x_1, x_2, ..., x_{10}|16\leq x_i \leq 256, 1\leq i \leq 10\}$ $\in$ $\mathcal{F}$, which increase the accuracy of the model in the short term.With simulating annealing algorithm\cite{17235}, we can find the approximate solutions.First, set the initial temperature $T$, the end temperature $T_E$, temperature decreasing rate $R_T$, and a random solution $f^*$.Second, create a model based on the parameter in the $f^*$, and train with $D$.We use cross entropy loss as loss function and Adam as optimization function.After training, we get the average loss of every epoch, $L^*$.Then, start the iteration by swap two of the parameters in $f^*$, get a new array $f^{**}$, train it with dataset, and get its average loss, $L^{**}$.After getting $L^*$ and $L^{**}$, we calculating the difference $\Delta L = L^{**} - L^*$.If $\Delta L \leq 0$, we update $f^* = f^{**}$.Otherwise, we use $e^{\frac{\Delta L}{T}}$ as the probability of the $f^{**}$ accepted as the new solution, get a random number $R^*$ $\in$ [1, 0] from random number generator, if $R^*$ is less than $e^{\frac{\Delta L}{T}}$, we update $f^* = f^{**}$.Then repeat the iteration, but replace the swapping with changing one of the number in $f^*$ to $n, 16 \leq n \leq 256$.
 \begin{equation}
    f^* = 
    \begin{cases}
    f^{**},  &\Delta L\le 0 \\
    f^{**},  &\Delta L \ge 0 \text{ and } R^*<e^{\frac{\Delta L}{T}} \\ 
    f^{*},   &\text{else}\\
    \end{cases}
\end{equation}

After the end of the iteration, multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then, we get the approximate solution$f=f^*$.Every 2 iteration, the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing can avoid solution stuck at local minimum.Use neural network found by NAS, we can now predict with untrained data with $80\%$ or so accuracy.
\section{Naive Bayes classifier}
